---
title: "Untitled"
output: pdf_document
---

CLEAR ALL AND LOAD PACKAGES
```{r,echo=FALSE,warning=FALSE,collapse=TRUE,eval=FALSE,tidy=TRUE}
# RESET -- Run to clear all data and start fresh...

pkgs = names(sessionInfo()$otherPkgs)
if (length(pkgs) > 0){
  pkgs = paste('package:', pkgs, sep = "")
  lapply(pkgs, detach, character.only = TRUE, unload = TRUE)
}

rm(list=ls())

library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=30),tidy=TRUE)

library(ggplot2)
library(car)
library(Rmisc)
library(lubridate) #   #   for setting up saved files so that filenames include today's date

daysDate <- format(now(), "%y%m%d")
F.ck.class <- function(x) data.frame(COL = seq_along(x), CLASS = sapply(x, class))
```


DATASETS
Data from Test Run Date: 03/05/2018 
```{r,tidy=TRUE}
file.data <- read.csv("combined_raw.csv", header = TRUE)
raw.data <- subset(file.data, Response.rt.box < 15)
F.ck.class(raw.data)
```

# COL   CLASS
# Block_Number             1 integer
# Trial_Number             2 integer
# Subject_Key_Box          3 integer
# Correct_Response         4  factor
# Answered_Correctly       5 logical
# Left_Zoid                6  factor
# Left_Zoid_Orientation    7 integer
# Right_Zoid               8  factor
# Right_Zoid_Orientation   9 integer
# Response.rt.box         10 numeric
# date                    11  factor
# frameRate               12 numeric
# SID                     13  factor

RAW DATA SELECTION
```{r,tidy=TRUE}
raw.data$deg.diff <- abs(raw.data$Left_Zoid_Orientation - raw.data$Right_Zoid_Orientation)
raw.data$deg.diff.level <- factor(raw.data$deg.diff, levels = c("0","90","180","270"))
same.data <- subset(raw.data, Correct_Response == "same")
same.data$deg.diff.level <- factor(same.data$deg.diff, levels = c("0","90","180","270"))

same.data$Left_Zoid  <- as.factor(same.data$Left_Zoid)

same.data_sz <- subset(same.data, Left_Zoid == "s" | Left_Zoid == "z")
same.data_jl <- subset(same.data, Left_Zoid == "j" | Left_Zoid == "l")
all_jl <- subset(raw.data, (Left_Zoid == "j" | Left_Zoid == "l")&(Right_Zoid == "j" | Right_Zoid == "l"))

all_jl$Type <- ifelse(all_jl$Left_Zoid == "j" & all_jl$Right_Zoid == "j", "J J", ifelse(all_jl$Left_Zoid == "j" & all_jl$Right_Zoid == "l", "J L", ifelse(all_jl$Left_Zoid == "l" & all_jl$Right_Zoid == "l", "L L", ifelse(all_jl$Left_Zoid == "l" & all_jl$Right_Zoid == "j", "L J", "error"))))

all_sz <- subset(raw.data, (Left_Zoid == "z" | Left_Zoid == "s")&(Right_Zoid == "z" | Right_Zoid == "s"))

all_sz$Type <- ifelse(all_sz$Left_Zoid == "z" & all_sz$Right_Zoid == "z", "Z Z", ifelse(all_sz$Left_Zoid == "z" & all_sz$Right_Zoid == "s", "Z S", ifelse(all_sz$Left_Zoid == "s" & all_sz$Right_Zoid == "s", "S S", ifelse(all_sz$Left_Zoid == "s" & all_sz$Right_Zoid == "z", "S Z", "error"))))

all_jl$Crit.level <- ifelse(all_jl$Crit.Score <= 7000, "low", ifelse((same.data$Crit.Score > 7000 & same.data$Crit.Score <= 15000), "mid", "high"))

all_jl$Crit.level <- factor(all_jl$Crit.level, levels = ordered(c("low", "mid", "high")))

all_sz$Crit.level <- ifelse(all_sz$Crit.Score <= 7000, "low", ifelse((same.data$Crit.Score > 7000 & same.data$Crit.Score <= 15000), "mid", "high"))

all_sz$Crit.level <- factor(all_sz$Crit.level, levels = ordered(c("low", "mid", "high")))

all_n = length(unique(same.data$SID))
same.data_lo <- subset(same.data, Crit.Score <= 7000)
lo_n = length(unique(same.data_lo$SID))
same.data_mid <- subset(same.data, Crit.Score > 7000 & Crit.Score <= 15000)
mid_n = length(unique(same.data_mid$SID))
same.data_hi <- subset(same.data, Crit.Score > 15000)
hi_n = length(unique(same.data_hi$SID))

sz.summ <- summarySE(data = same.data_sz, measurevar = "Response.rt.box", groupvars = c("Left_Zoid", "deg.diff.level"))
jl.summ <- summarySE(data = same.data_jl, measurevar = "Response.rt.box", groupvars = c("Left_Zoid", "deg.diff.level"))

sz.summ.sid <- summarySE(data = same.data_sz, measurevar = "Response.rt.box", groupvars = c("Left_Zoid", "deg.diff.level", "SID", "Crit.Score"))
jl.summ.sid <- summarySE(data = same.data_jl, measurevar = "Response.rt.box", groupvars = c("Left_Zoid", "deg.diff.level", "SID", "Crit.Score"))

shape.summ <- summarySE(data = same.data, measurevar = "Response.rt.box", groupvars = c("Left_Zoid", "deg.diff.level"))
shape.summ.hi <- summarySE(data = same.data_hi, measurevar = "Response.rt.box", groupvars = c("Left_Zoid", "deg.diff.level"))
shape.summ.mid <- summarySE(data = same.data_mid, measurevar = "Response.rt.box", groupvars = c("Left_Zoid", "deg.diff.level"))
shape.summ.lo <- summarySE(data = same.data_lo, measurevar = "Response.rt.box", groupvars = c("Left_Zoid", "deg.diff.level"))

jllj.summ <- summarySE(data = all_jl[!is.na(all_jl$Crit.Score),], measurevar = "Response.rt.box", groupvars = c("Type", "deg.diff.level", "Crit.level"))
szzs.summ <- summarySE(data = all_sz[!is.na(all_sz$Crit.Score),], measurevar = "Response.rt.box", groupvars = c("Type", "deg.diff.level", "Crit.level"))

raw.data$Block_Number  <- as.factor(raw.data$Block_Number)

# NA's
## first look at the NAs in the entire dataset
NAs_zr <- raw.data[rowSums(is.na(raw.data)) > 0,]
## good, no NAs

library("plyr")
library("dplyr")

SID.data <- list()
for(this.SID in unique(raw.data$SID))
{
  SID.data[[length(SID.data)+1]] <- raw.data[which(raw.data$SID==this.SID),]
}

tzr_summary <- ddply(raw.data, .(Block_Number, Correct_Response), function (x){
	total_blocks = length(unique(x$Block_Number))
	trials_per_block = length(unique(x$Trial_Number))
	m_rt = mean(x$Response.rt.box)
	med_rt = median(x$Response.rt.box)
	correct = mean(x$Answered_Correctly)
	sid = x$SID
	data.frame(total_blocks, trials_per_block, m_rt, med_rt, correct, sid)
})

SID.tzr.summ <- list()
for(this.data in SID.data)
{
  this.tzr.summary <- ddply(this.data, .(Block_Number, Correct_Response), function (x){
	total_blocks = length(unique(x$Block_Number))
	trials_per_block = length(unique(x$Trial_Number))
	m_rt = mean(x$Response.rt.box)
	med_rt = median(x$Response.rt.box)
	correct = mean(x$Answered_Correctly)
	sid = x$SID
	score = x$Crit.Score
	data.frame(total_blocks, trials_per_block, m_rt, med_rt, correct, sid, score)
  })
  SID.tzr.summ[[length(SID.tzr.summ)+1]] <- this.tzr.summary
  
}


F.ck.class(tzr_summary)

for(this_summ in SID.tzr.summ)
{
  F.ck.class(this_summ)
}

```

PLOTTING
```{r,tidy=TRUE}


plt.2a <- ggplot(jl.summ, aes(x = deg.diff.level, y = Response.rt.box, group = Left_Zoid, color = Left_Zoid))
plt.2a + stat_summary(fun.y = mean, geom = "line") + stat_summary(fun.y = mean, geom = "point") + geom_errorbar(aes(ymin=Response.rt.box-ci, ymax=Response.rt.box+ci), width = 0.05, position=position_dodge(width=0.3)) + ylim(0, 2) + theme_bw() + labs(title = "J/L Same Response Time", subtitle = paste("All paritcipants"), x = "Rel. Degree Differnece", y = "Response Time (s)")

for(indi in unique(jl.summ.sid$SID))
{
  plt.7b <- ggplot(jl.summ.sid[jl.summ.sid$SID == indi,], aes(x = deg.diff.level, y = Response.rt.box, group = Left_Zoid, color = Left_Zoid)) + geom_line() + geom_point() + ylim(0, 2) +
	theme_bw() +
  labs(title = "J/L Same Response Time (Individual)", subtitle = paste("SID: ", indi, "Crit. Score = ", jl.summ.sid[jl.summ.sid$SID == indi,]$Crit.Score), x = "Rel. Degree Differnece", y = "Response Time (s)")
  png(paste(indi, ".png"))
  print(plt.7b)
  dev.off()
}

for(indi in unique(sz.summ.sid$SID))
{
  plt.7b <- ggplot(sz.summ.sid[jl.summ.sid$SID == indi,], aes(x = deg.diff.level, y = Response.rt.box, group = Left_Zoid, color = Left_Zoid)) + geom_line() + geom_point() + ylim(0, 2) +
	theme_bw() +
  labs(title = "J/L Same Response Time (Individual)", subtitle = paste("SID: ", indi, "Crit. Score = ", jl.summ.sid[jl.summ.sid$SID == indi,]$Crit.Score), x = "Rel. Degree Differnece", y = "Response Time (s)")
  png(paste(indi, ".png"))
  print(plt.7b)
  dev.off()
}

plt.8a <- ggplot(sz.summ, aes(x = deg.diff.level, y = Response.rt.box, group = Left_Zoid, color = Left_Zoid))
plt.8a + stat_summary(fun.y = mean, geom = "line") + stat_summary(fun.y = mean, geom = "point") + geom_errorbar(aes(ymin=Response.rt.box-ci, ymax=Response.rt.box+ci), width = 0.05, position=position_dodge(width=0.3)) + ylim(0, 2) + theme_bw() + labs(title = "S/Z Same Response Time", subtitle = paste("All paritcipants"), x = "Rel. Degree Differnece", y = "Response Time (s)")

plt.shape <- ggplot(shape.summ, aes(x = deg.diff.level, y = Response.rt.box, group = Left_Zoid, color = Left_Zoid))
plt.shape + geom_line() + geom_point(size = 2.5) + ylim(0.5, 1.6) + theme_bw() + labs(title = "Response Time by Zoid and Orientation", subtitle = paste("all players, n =", all_n), y = "Response Time", x = "Abs. Degree Difference", colour = "Zoid Type") + geom_errorbar(aes(ymin=Response.rt.box-ci, ymax=Response.rt.box+ci), width = 0.2, position=position_dodge(width=0.3))

plt.jl <- ggplot(jllj.summ, aes(x = deg.diff.level, y = Response.rt.box, group = Type))
plt.jl + geom_line() + geom_point(size = 2.5) + ylim(0.5, 2.5) + theme_bw() + labs(title = "Response Time with all J/L pairs by high/mid/low skill levels", y = "Response Time", x = "Abs. Degree Difference") + geom_errorbar(aes(ymin=Response.rt.box-ci, ymax=Response.rt.box+ci), width = 0.2) + facet_grid(Crit.level~Type)

plt.sz <- ggplot(szzs.summ, aes(x = deg.diff.level, y = Response.rt.box, group = Type))
plt.sz + geom_line() + geom_point(size = 2.5) + ylim(0.2, 3) + theme_bw() + labs(title = "Response Time with all S/Z pairs by high/mid/low skill levels", y = "Response Time", x = "Abs. Degree Difference") + geom_errorbar(aes(ymin=Response.rt.box-ci, ymax=Response.rt.box+ci), width = 0.2) + facet_grid(Crit.level~Type)

plt.shapelo <- ggplot(shape.summ.lo, aes(x = deg.diff.level, y = Response.rt.box, group = Left_Zoid, color = Left_Zoid))
plt.shapelo + geom_line() + geom_point(size = 2.5) + ylim(0.5, 1.6) + theme_bw() + labs(title = "Response Time by Zoid and Orientation", subtitle = paste("low skill players (Crit. Score 0~7000), n =", lo_n), y = "Response Time", x = "Abs. Degree Difference", colour = "Zoid Type") + geom_errorbar(aes(ymin=Response.rt.box-ci, ymax=Response.rt.box+ci), width = 0.2, position=position_dodge(width=0.3))

plt.shapemid <- ggplot(shape.summ.mid, aes(x = deg.diff.level, y = Response.rt.box, group = Left_Zoid, color = Left_Zoid))
plt.shapemid + geom_line() + geom_point(size = 2.5) + ylim(0.5, 1.6) + theme_bw() + labs(title = "Response Time by Zoid and Orientation", subtitle = paste("mid skill players (Crit. Score 7000~15000), n =", mid_n), y = "Response Time", x = "Abs. Degree Difference", colour = "Zoid Type") + geom_errorbar(aes(ymin=Response.rt.box-ci, ymax=Response.rt.box+ci), width = 0.2, position=position_dodge(width=0.3))

plt.shapehi <- ggplot(shape.summ.hi, aes(x = deg.diff.level, y = Response.rt.box, group = Left_Zoid, color = Left_Zoid))
plt.shapehi + geom_line() + geom_point(size = 2.5) + ylim(0.5, 1.6) + theme_bw() + labs(title = "Response Time by Zoid and Orientation", subtitle = paste("high skill players (Crit. Score 15000~), n =", hi_n), y = "Response Time", x = "Abs. Degree Difference", colour = "Zoid Type") + geom_errorbar(aes(ymin=Response.rt.box-ci, ymax=Response.rt.box+ci), width = 0.2, position=position_dodge(width=0.3))

plt.9b <- ggplot(jl.summ, aes(x = deg.diff.level, y = Response.rt.box, group = Left_Zoid, color = Left_Zoid))
plt.9b + stat_summary(fun.y = mean, geom = "line") + stat_summary(fun.y = mean, geom = "point") + geom_errorbar(aes(ymin=Response.rt.box-ci, ymax=Response.rt.box+ci), width = 0.05, position=position_dodge(width=0.3)) + ylim(0, 2) + theme_bw() 

raw.data$Block_Number  <- as.factor(raw.data$Block_Number)

#   PROPORTION CORRECT BY SAME VS DIFF BY BLOCK
tzr_propCorrect_by_blk <- ggplot(tzr_summary, aes(x=Block_Number, y=correct, group=Correct_Response, color=Correct_Response)) +
	geom_line() +
	geom_point() +
	scale_shape_manual(values=c(17,19)) +
	scale_color_manual(values=c("darkred", "darkblue")) +
	annotate(geom="text", x=4, y=0.9125, label = "Proportion Correct for Same vs Different", color = "darkgreen") +
	theme_bw()
tzr_propCorrect_by_blk

#	MEDIAN RT BY SAME VS DIFF RESPONSE BY BLOCK
tzr_medRT_by_SameDif_by_blk <- ggplot(tzr_summary, aes(x=Block_Number, y=med_rt, group=Correct_Response, color=Correct_Response)) +
	geom_line() +
	geom_point() +
	scale_shape_manual(values=c(17,19)) +
	scale_color_manual(values=c("darkred", "darkblue")) +
	annotate(geom = "text", x=6, y=1.5, label = "Median Response Time for Correct Response", color = "darkgreen") +
	theme_bw()
tzr_medRT_by_SameDif_by_blk

#   SUBJECT ACCURACY
for (this.summ in SID.tzr.summ)
{
  subject_acc <- ggplot(this.summ, aes(x=Block_Number, y=correct, group=Correct_Response, color=Correct_Response)) +
	geom_line() +
	geom_point() +
	scale_shape_manual(values=c(17,19)) +
	scale_color_manual(values=c("darkred", "darkblue")) +
	theme_bw() +
  labs(title = "Proportion Correct for Same vs Different (Individual)", subtitle = paste("SID: ", this.summ$sid, "Crit. Score = ", this.summ$score))
  png(paste(this.summ$sid, ".png"))
  print(subject_acc)
  dev.off()
}
for (this.summ in SID.tzr.summ)
{
  subj_time <- ggplot(this.summ, aes(x=Block_Number, y=med_rt, group=Correct_Response, color=Correct_Response)) +
	geom_line() +
	geom_point() +
	scale_shape_manual(values=c(17,19)) +
	scale_color_manual(values=c("darkred", "darkblue")) +
	labs(title = "Proportion Correct for Same vs Different (Individual)", subtitle = paste("SID: ", this.summ$sid, "Crit. Score = ", this.summ$score)) +
	theme_bw()
png(paste(this.summ$sid, ".png"))
  print(subj_time)
  dev.off()
}


```
